### 2014-01-31 manuscripts/reply/reply-main.tex
Minor edits to dpp and reply manuscripts.
Updating reply manuscript.
Incorporating comments from Adam and adding some missing `linenomath`
environments to paragraphs with equations.

\msb \citep{Huang2011} uses approximate Bayesian computation (ABC) to estimate
the distribution of divergence times among co-distributed pairs of taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact values of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
The exact divergence time is therefore often viewed as a nuisance parameter,
and researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       support models with few divergence events shared across taxa. Thus, the
       primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}

This is not surprising given the rich statistical literature that shows that
model marginal likelihoods are quite sensitive to the priors used in Bayesian
model selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.
Accordingly, \citet{Oaks2012} suggest the primary cause of spurious support
for models with few divergence parameters is the greater marginal likelihoods
of these models under vague uniform priors, relative to more parameter-rich
models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density imposed by the uniformly distributed prior on divergence times.
Note, this is a statistical issue, extrinsic to \msb, and does not question the
soundness of the numerical approximation machinery of \msb.

@@

Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is questionable.
In Bayesian model choice, the primary goal is not to estimate parameters, but
to estimate the relative probabilities of candidate models.
In a simple example where two candidate models, $M_1$ and $M_2$, are being
compared, the goal is to estimate the posterior probabilities of these two
models.
Again, we can use Bayes' rule to calculate this as
\begin{equation}
    p(M_1 \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given
    M_1)p(M_1)}{p(\alignment{i}{} \given M_1)p(M_1) + p(\alignment{i}{} \given
    M_2)p(M_2)}.
    \label{eq:bayesmodelchoice}
\end{equation}
By comparing Equations \ref{eq:bayesrule} and \ref{eq:bayesmodelchoice}, we
see fundamental differences between Bayesian parameter estimation and
model choice.
In Equation \ref{eq:bayesrule}, we see that the posterior density of any
state $\myTheta{}$ of the model, is the prior density updated by the
probability of the data given the state $\myTheta{}$ (the likelihood of
$\myTheta{}$).
The integral over the entire parameter space of the model, which is defined by
the priors, only appears as a normalizing constant in the denominator.
Thus, as long as the prior distribution contains the values of $\myTheta{}$
that maximize the probability of the data (i.e., the maximum likelihood) and
the data are strongly informative relative to the prior, the values of the
parameters that maximize the posterior distribution will be relatively robust
to prior choice, even if the posterior distribution is technically incorrect
due to using the data to inform the priors.
This is why empirical Bayes can work well for estimating the values of model
parameters.

@@

This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by informing priors with the same data to be analyzed.
For empirical Bayesian parameter estimation, the objective is that by giving the
data more weight relative to the prior, the posterior distribution will be
peaked near the true value(s) of the model's parameter(s).
There is no such justification for empirical Bayesian model choice, because
there are no true values for the model probabilities being estimated.
By using the data twice, we fail to account for prior uncertainty and mislead
our posterior beliefs in the models being compared; we will be over confident
in some models and under confident in others.
Nonetheless, empirical Bayesian model choice does perform well for some
inference problems.
Particularly, in cases where large aggregate data sets are used for many
parallel model-choice problems simultaneously, pooling information to inform
priors can lead to favorable group-wise frequentist coverage across tests
\citep{Efron2008}.

These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times each, and so we decide to use these data in specifying
a beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin of interest $N=10$ times, $y=3$ of which
land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, we can calculate the
posterior probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior
and data.

@@

Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret.

@@

Given the theoretical and practical issues with empirical Bayes approaches to
Bayesian model choice, it is clear why one should use caution before overly
criticizing an investigator's choice of priors \emph{after} having seen the
resulting posterior.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a
large amount of uncertainty regarding the divergence times of the 22 population
pairs under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013,Rafe2013AREES,Siler2014kikuchii}.
When limited to uniformly distributed priors, the alternative to priors that
reflect prior uncertainty, as shown above, is to risk excluding the true values
one seeks to estimate.
However continuous distributions perhaps more appropriate as priors for
positive real-valued parameters have been shown to greatly reduce spurious
support for clustered divergence models while allowing prior uncertainty to be
accommodated \citep{Oaks2014dpp}.

>>>>

\msb \citep{Huang2011} uses approximate Bayesian computation (ABC) to estimate
the distribution of divergence times among co-distributed pairs of taxa.
It approximates a posterior probability over models that range from a single
divergence-time parameter (i.e., simultaneous divergence of all pairs of taxa)
to the fully generalized model in which each pair of taxa diverged at a
unique time.
A full description of the model is given in \citet{Oaks2012}.
Frequently, the exact values of the divergence times are hard 
to determine because researchers typically lack precise knowledge 
of the rate at which substitutions occur.
The exact divergence time is therefore often viewed as a nuisance parameter,
and researchers focus on the number of divergence events.
The papers of \citet{Oaks2012} and \citet{Hickerson2013} are in agreement
on the fundamental methodological point about the model selection performed in \msb:
\begin{itemize}
   \item The use of vague priors on the divergence-time parameters can lead to
       support for models with few divergence events shared across taxa. Thus,
       the primary inference enabled by the approach is very sensitive to the
       priors on divergence times.
\end{itemize}

This is not surprising given the rich statistical literature that shows that
marginal likelihoods are very sensitive to the priors used in Bayesian model
selection
\citep[e.g.,][]{Jeffreys1939,Lindley1957}.
Accordingly, \citet{Oaks2012} suggest the primary cause of spurious support
for models with few divergence parameters is the greater marginal likelihoods
of these models under vague uniform priors, relative to more parameter-rich
models.
Models with more divergence-time parameters integrate over \emph{much} greater
parameter space with low probability of producing the data, yet relatively high
prior density imposed by the uniformly distributed prior on divergence times.
Note, this is a statistical issue, extrinsic to \msb, and does not question the
soundness of the numerical approximation machinery of \msb.

@@

\begin{linenomath}
Whereas empirical Bayes approaches can provide powerful methods for parameter
estimation, a theoretical justification for empirical Bayes approaches to model
choice is questionable.
In Bayesian model choice, the primary goal is not to estimate parameters, but
to estimate the relative probabilities of candidate models.
In a simple example where two candidate models, $M_1$ and $M_2$, are being
compared, the goal is to estimate the posterior probabilities of these two
models.
Again, we can use Bayes' rule to calculate this as
\begin{equation}
    p(M_1 \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given
    M_1)p(M_1)}{p(\alignment{i}{} \given M_1)p(M_1) + p(\alignment{i}{} \given
    M_2)p(M_2)}.
    \label{eq:bayesmodelchoice}
\end{equation}
By comparing Equations \ref{eq:bayesrule} and \ref{eq:bayesmodelchoice}, we
see fundamental differences between Bayesian parameter estimation and
model choice.
In Equation \ref{eq:bayesrule}, we see that the posterior density of any
state $\myTheta{}$ of the model, is the prior density updated by the
probability of the data given the state $\myTheta{}$ (the likelihood of
$\myTheta{}$).
The integral over the entire parameter space of the model, which is defined by
the priors, only appears as a normalizing constant in the denominator.
Thus, as long as the prior distribution contains the values of $\myTheta{}$
that maximize the probability of the data (i.e., the maximum likelihood) and
the data are strongly informative relative to the prior, the values of the
parameters that maximize the posterior distribution will be relatively robust
to prior choice, even if the posterior distribution is technically incorrect
due to using the data to inform the priors.
This is why empirical Bayes can work well for estimating the values of model
parameters.
\end{linenomath}

@@

This complicates the meaning of model posterior probabilities when Bayes' rule
is violated by informing priors with the same data to be analyzed.
For empirical Bayesian parameter estimation, the objective is that by giving the
data more weight relative to the prior, the posterior distribution will be
peaked near the true value(s) of the model's parameter(s).
There is no such justification for empirical Bayesian model choice, because
there are no true values for the model probabilities being estimated.
By using the data twice, we fail to account for prior uncertainty and mislead
our posterior beliefs in the models being compared; we will be over confident
in some models and under confident in others.
Nonetheless, empirical Bayesian model choice does perform well for some
model-choice problems.
Particularly, in cases where large aggregate data sets are used for many
parallel model-choice problems simultaneously, pooling information to inform
priors can lead to favorable group-wise frequentist coverage across tests
\citep{Efron2008}.

\begin{linenomath}
These distinctions between Bayesian parameter estimation and model choice can
be illustrated with a simple example.
Let us say we are interested in the fairness of a particular coin, and we
denote the unknown probability of it landing heads as \myTheta{}.
More specifically, we are interested in the probability of two models, $M_1$
and $M_2$.
In both models the outcomes of flipping the coin are assumed to be binomially
distributed, but under $M_1$ the coin is weighted toward landing heads (i.e.,
$\myTheta{} > 0.5)$), whereas under $M_2$, the coin is weighted toward landing
tails (i.e., $\myTheta{} < 0.5$).
We already have data from flipping a different coin 20 times that landed both
heads and tails 10 times each, and so we decide to use these data in specifying
a beta prior on fairness of the new coin of $beta(a=10, b=10)$
(Figure~\ref{figCoinFlip}).
We collect data by flipping the coin of interest $N=10$ times, $y=3$ of which
land heads.
Given the beta distribution is a conjugate prior for a binomial likelihood, the
posterior distribution has the nice analytical form $\theta \given y,N \sim
beta(a + y, b + N - y)$, which for the new dataset is simply $beta(13, 17)$
(Figure~\ref{figCoinFlip}).
The maximum a posteriori (MAP) estimate of the probability of heads is 0.429,
and following Equation~\ref{eq:marginallikelhiood} the marginal likelihoods of
our models of interest are
\begin{equation}
    p(y=3, N=10 \given M_1) = \int_{0.5}^{1} p(y=3, N=10 \given
    \myTheta{}, M_1)p(\myTheta{} \given M_1) d\myTheta{} \approx 0.029,
\end{equation}
and
\begin{equation}
    p(y=3, N=10 \given M_2) = \int_{0}^{0.5} p(y=3, N=10 \given
    \myTheta{}, M_2)p(\myTheta{} \given M_2) d\myTheta{} \approx 0.097.
\end{equation}
Given the models have equal probability under our prior, we can calculate the
posterior probability of Model 1 as
\begin{equation}
    p(M_1 \given y=3, N=10) = \frac{p(y=3, N=10 \given M_1)}{p(y=3, N=10 \given
    M_1) + p(y=3, N=10 \given M_2)} \approx 0.23.
\end{equation}
This is the correct posterior probability of Model 1 given our prior
and data.
\end{linenomath}

@@

Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude true divergence
times, making their results difficult to interpret.

@@

Given the theoretical and practical issues with empirical Bayes approaches to
Bayesian model choice, it is clear why one should use caution before overly
criticizing an investigator's choice of priors \emph{after} having seen the
resulting posterior.
As discussed by \citet{Oaks2012}, prior to analyzing the data, there was a
large amount of uncertainty regarding the divergence times of the 22 population
pairs under study.
Two of these pairs represent distinct species, and the taxonomy of many groups
in the Philippines has repeatedly been shown to mask deeply divergent lineages
\citep{RafeDiesmosAlcala2008,Linkem2010,Siler2010,Welton2010,Siler2011HerpMonographs,
Siler2011,Siler2012,RafeStuart2012,LinkemBrown2013,Rafe2013AREES,Siler2014kikuchii}.
When limited to uniformly distributed priors, the alternative to priors that
reflect prior uncertainty, as shown above, is to risk excluding the true values
one seeks to estimate.
However, continuous distributions more appropriate as priors for positive
real-valued parameters have been shown to greatly reduce spurious support for
clustered divergence models while allowing prior uncertainty to be accommodated
\citep{Oaks2014dpp}.
